### 2013-06-26 latex/SupportingText.tex
Updated SupportingText.tex

@@

\begin{center}
\footnotesize
\begin{tabular}{lccccccccc}
Residue & max-emp-100 & max-emp-97 & max-emp-80 & max-emp-gen & & max-theo-100 & max-theo-97 & max-theo-80 & max-theo-gen\\
\hline Alanine   & $121$ & $121$ & $121$ & $121$ & & $138$ & $129$ & $128$ & $132$\\
Arginine         & $265$ & $265$ & $265$ & $265$ & & $285$ & $274$ & $274$ & $280$\\
Asparagine       & $187$ & $187$ & $187$ & $187$ & & $204$ & $195$ & $193$ & $199$\\
Aspartate        & $187$ & $187$ & $187$ & $187$ & & $204$ & $193$ & $192$ & $197$\\
Cysteine         & $148$ & $148$ & $133$ & $148$ & & $169$ & $167$ & $157$ & $167$\\
Glutamate        & $214$ & $214$ & $214$ & $214$ & & $233$ & $223$ & $222$ & $227$\\
Glutamine        & $214$ & $214$ & $214$ & $214$ & & $234$ & $225$ & $224$ & $228$\\
Glycine          & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & & $114$ & $104$ & $104$ & $109$\\
Histidine        & $216$ & $216$ & $216$ & $216$ & & $213$ & $209$ & $209$ & $209$\\
Isoleucine       & $195$ & $195$ & $195$ & $195$ & & $208$ & $197$ & $196$ & $201$\\
Leucine          & $191$ & $191$ & $191$ & $191$ & & $211$ & $201$ & $199$ & $205$\\
Lysine           & $230$ & $230$ & $229$ & $230$ & & $246$ & $236$ & $235$ & $240$\\
Methionine       & $203$ & $203$ & $203$ & $203$ & & $227$ & $224$ & $218$ & $226$\\
Phenylalanine    & $228$ & $228$ & $226$ & $228$ & & $251$ & $240$ & $236$ & $244$\\
Proline          & $154$ & $154$ & $154$ & $154$ & & $166$ & $159$ & $157$ & $164$\\
Serine           & $143$ & $143$ & $143$ & $143$ & & $161$ & $155$ & $150$ & $158$\\
Threonine        & $163$ & $163$ & $161$ & $163$ & & $182$ & $172$ & $171$ & $176$\\
Tryptophan       & $264$ & $264$ & $262$ & $264$ & & $295$ & $285$ & $282$ & $293$\\
Tyrosine         & $255$ & $255$ & $255$ & $255$ & & $274$ & $263$ & $262$ & $266$\\
Valine           & $166$ & $165$ & $165$ & $166$ & & $184$ & $174$ & $173$ & $177$\\
\hline
\end{tabular}
\end{center}

\begin{center}
\footnotesize
\begin{tabular}{lcccccccc}
Residue & pop-97 & pop-80 \\
\hline Alanine   & $4$ & $47$ \\
Arginine         & $2$ & $23$ \\
Asparagine       & $2$ & $15$ \\
Aspartate        & $3$ & $20$ \\
Cysteine         & $0$ & $\phantom{0}5$ \\
Glutamate        & $3$ & $34$ \\
Glutamine        & $2$ & $18$ \\
Glycine          & $2$ & $15$ \\
Histidine        & $1$ & $\phantom{0}9$ \\
Isoleucine       & $6$ & $40$ \\
Leucine          & $7$ & $59$ \\
Lysine           & $3$ & $27$ \\
Methionine       & $0$ & $\phantom{0}8$ \\
Phenylalanine    & $2$ & $20$ \\
Proline          & $7$ & $80$ \\
Serine           & $2$ & $27$ \\
Threonine        & $3$ & $33$ \\
Tryptophan       & $0$ & $\phantom{0}8$ \\
Tyrosine         & $2$ & $18$ \\
Valine           & $7$ & $50$ \\
\hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\scriptsize
\begin{tabular}{lccccccccc}
 & \multicolumn{4}{c}{Empirical} &&\multicolumn{4}{c}{Theoretical}\\\cline{2-5}\cline{7-10}
Residue          & all & allowed & core & generous & & all & allowed & core & generous\\
\hline Alanine   & $121$ & $121$ & $121$ & $121$ & & $138$ & $129$ & $128$ & $132$\\
Arginine         & $265$ & $265$ & $265$ & $265$ & & $285$ & $274$ & $274$ & $280$\\
Asparagine       & $187$ & $187$ & $187$ & $187$ & & $204$ & $195$ & $193$ & $199$\\
Aspartate        & $187$ & $187$ & $187$ & $187$ & & $204$ & $193$ & $192$ & $197$\\
Cysteine         & $148$ & $148$ & $133$ & $148$ & & $169$ & $167$ & $157$ & $167$\\
Glutamate        & $214$ & $214$ & $214$ & $214$ & & $233$ & $223$ & $222$ & $227$\\
Glutamine        & $214$ & $214$ & $214$ & $214$ & & $234$ & $225$ & $224$ & $228$\\
Glycine          & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & & $114$ & $104$ & $104$ & $109$\\
Histidine        & $216$ & $216$ & $216$ & $216$ & & $213$ & $209$ & $209$ & $209$\\
Isoleucine       & $195$ & $195$ & $195$ & $195$ & & $208$ & $197$ & $196$ & $201$\\
Leucine          & $191$ & $191$ & $191$ & $191$ & & $211$ & $201$ & $199$ & $205$\\
Lysine           & $230$ & $230$ & $229$ & $230$ & & $246$ & $236$ & $235$ & $240$\\
Methionine       & $203$ & $203$ & $203$ & $203$ & & $227$ & $224$ & $218$ & $226$\\
Phenylalanine    & $228$ & $228$ & $226$ & $228$ & & $251$ & $240$ & $236$ & $244$\\
Proline          & $154$ & $154$ & $154$ & $154$ & & $166$ & $159$ & $157$ & $164$\\
Serine           & $143$ & $143$ & $143$ & $143$ & & $161$ & $155$ & $150$ & $158$\\
Threonine        & $163$ & $163$ & $161$ & $163$ & & $182$ & $172$ & $171$ & $176$\\
Tryptophan       & $264$ & $264$ & $262$ & $264$ & & $295$ & $285$ & $282$ & $293$\\
Tyrosine         & $255$ & $255$ & $255$ & $255$ & & $274$ & $263$ & $262$ & $266$\\
Valine           & $166$ & $165$ & $165$ & $166$ & & $184$ & $174$ & $173$ & $177$\\
\hline
\end{tabular}
\end{center}

\begin{center}
\begin{tabular}{lcccccccc}
Residue & pop-97 & pop-80 \\
\hline Alanine   & $4$ & $47$ \\
Arginine         & $2$ & $23$ \\
Asparagine       & $2$ & $15$ \\
Aspartate        & $3$ & $20$ \\
Cysteine         & $0$ & $\phantom{0}5$ \\
Glutamate        & $3$ & $34$ \\
Glutamine        & $2$ & $18$ \\
Glycine          & $2$ & $15$ \\
Histidine        & $1$ & $\phantom{0}9$ \\
Isoleucine       & $6$ & $40$ \\
Leucine          & $7$ & $59$ \\
Lysine           & $3$ & $27$ \\
Methionine       & $0$ & $\phantom{0}8$ \\
Phenylalanine    & $2$ & $20$ \\
Proline          & $7$ & $80$ \\
Serine           & $2$ & $27$ \\
Threonine        & $3$ & $33$ \\
Tryptophan       & $0$ & $\phantom{0}8$ \\
Tyrosine         & $2$ & $18$ \\
Valine           & $7$ & $50$ \\
\hline
\end{tabular}
\end{center}

@@
